

%\subsection{Sequentiel version}
%in this first optimization Frozar you are suggested to put the improvement due to the new data structure you took
In the sequential version, the algorithm presented is an asynchronous Tutte one. In fact, there is a second approach, the synchronous Tutte version. The difference between the two approaches is :
\begin{itemize}
\item in asynchronous version: each movement is applied directy after being computed
\item in synchronous version: all movement are computed before being applied
\end{itemize}
In the sequential version, the synchronous approach does not present
benefits. It is more convenient to consider neighbors movement.

In the parallel version, the synchronous approach may be interesting in
order to reduce critical sections. For the both parallel approach use the
OpenMP library.
\\
The complexity these two algorithms is roughly $\mathit{O(\frac{n}{p})}$
with $n = |V|$ and $p$ is the number of processeurs.
\\

\subsection{Asynchronous parallel version}
% in this optimization Ozenati you are suggested to talk about the
% asynchronous implementation (if faster than the others) with graph
% coloration
\input{src/graph_coloring}

\subsection{Synchronous parallel version}

The parallel synchronous version of the Tutte algorithm is easier to
implement then the parallel asynchronous. For this version, one
does not need to compute a coloring separation.
\\

During an iteration, the new coordinates of all nodes on the graph are saved in a table instead of being
directly applied. At the end of an iteration, all upgrades are applied. In
this approach, two nodes can be computed independently in parallel. 
\\

Consequently, for an iteration, the set of nodes to visit can be separated in different
subsets. Each of these subsets is independent and can be computed by
different threads in parallel. The separation is static, i.e. the number of
element of each subset is equal to $nb\_node / nb\_thread$.

