\documentclass[11pt]{article}
\usepackage[usenames]{color}

\title{\color{blue}\jobname.tex}
\author{Bent Petersen}
\date{Oct 24, 2000}

\pagestyle{plain}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2.0ex plus 0.6ex minus 0.4ex}

\begin{document}
\maketitle
\thispagestyle{empty}

The easiest way to use color text in \LaTeXe{} is to use the color
package. You load the color package in your preamble as usual
\begin{verbatim}
\documentclass[11pt]{article}
\usepackage[usenames]{color}
\end{verbatim}
Here the option [usenames] causes the definitions for the 68 colors
known to dvips (see next page) to be preloaded. Those colors can then
be specified by name. For example \verb={\color{BrickRed} BrickRed}= 
produces {\color{red} red}. Alternately one can use the 
command 
\begin{verbatim}
\textcolor{BrickRed}{this is BrickRed}
\end{verbatim}
which produces \textcolor{red}{this is red}.

If the 68 predefined colors do not suffice, or if you do not want
to load the definitions of all of them, you may define your own
custom colors.

Here is a dark blue defined in terms of the RGB (red, green, blue) color model.
\begin{verbatim}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\begin{center}
{\color{MyDarkBlue}This color is MyDarkBlue}
\end{center}
\end{verbatim}
%%
\definecolor{MyDarkBlue}{rgb}{0.1,0,0.55}
\begin{center}
{\color{MyDarkBlue}This color is MyDarkBlue}
\end{center}
%%
Once we have defined the new color we can use it anywhere in
the current document. For example, 
\verb=\textcolor{MyDarkBlue}{a nice blue}= produces
\textcolor{MyDarkBlue}{a nice blue}.

Custom colors may also be defined in terms of the CMYK 
(cyan, magenta, yellow, black) 
color model. Here is a light magenta.
%%
\begin{verbatim}
\definecolor{MyLightMagenta}{cmyk}{0.1,0.8,0,0.1}
\begin{center}
{\color{MyLightMagenta}This color is MyLightMagenta}
\end{center}
\end{verbatim}
%%
\definecolor{MyLightMagenta}{cmyk}{0.1,0.8,0,0.1}
\begin{center}
{\color{MyLightMagenta}This color is MyLightMagenta}
\end{center}

\begin{center}\large
The 68 standard colors known to dvips\vspace{0.5ex}
\begin{tabular}{|l|l|l|l|l|}
\hline
{\color{yellow} yellow}&
{\color{green} green}&
{\color{white} white}&
{\color{black} Black}&
{\color{blue} Blue}\\ \hline 
\end{tabular}
\end{center}

\end{document}
